### 2015-12-11 paper/3-features.tex
Rewrite section 3.1 introduction

\subsection{Synchronization protocols}
We have previously shown that different synchronization protocols exist, with each of them being optimized for a specific kind of model.
As no single synchronization protocol is ideal, a general purpose simulation tool should support multiple situations.
Currently, however, most parallel simulation tools chose only a single synchronization protocol due to the inherent differences between these approaches.
An uninformed choice on which to implement is insufficient, as performance is likely to be bad.
We therefore argue that a real general purpose simulation tool should support sequential, conservative, and optimistic synchronization.

Each of them is applicable in specific model configurations.
Conservative synchronization is ideal when high lookahead exists between different nodes, and barely any blocking is necessary.
Optimistic synchronization is ideal when lookahead is unpredictable, or there are rare (almost) instantaneous events.
Finally, sequential simulation is still required for models where parallelism is bad, causing significant overhead.

>>>>

\subsection{Synchronization protocols}
We previously explained the existence of different synchronization protocols exist, each optimized for a specific kind of model.
As no single synchronization protocol is ideal for all models, a general purpose simulation tool should support multiple protocols.
Currently, most parallel simulation tools chose only a single synchronization protocol due to the inherent differences between protocols.
An uninformed choice on which one to implement is insufficient, as performance will likely be bad.
We argue that a real general purpose simulation tool should support sequential, conservative, and optimistic synchronization, as is the case for dxex.

These different protocols relate to three different model characteristics.
Conservative synchronization for when high lookahead exists between different nodes, and barely any blocking is necessary.
Optimistic synchronization for when lookahead is unpredictable, or there are rare (almost) instantaneous events.
Finally, sequential simulation is still required for models where parallelism is bad, where all protocols actually slow down simulation.
